---
title: "02 - Prepare loan input files for stress testing corporate loan books"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette describes in detail, how to prepare the intermediate input files
needed to run the climate transition risk stress test for a corporate loan book.

## Assumptions

In order to keep this vignette concise, we assume the following has been done:

1. R and RStudio are installed.
2. All required R packages are installed, specifically
`r2dii.climate.stress.test`. Note that this may require installing additional
packages. You will be prompted to install these in case any are missing.
3. The user has successfully run at least the matching part of PACTA for Banks
to produce the relevant project-specific raw input files.
4. The user has obtained all relevant input files as described in the pdf manual.
5. The input files are organized in a folder structure consistent with the one
described in the vignette [Set up project directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).

## Running the Loan Book Preparation

```{r setup}
library(r2dii.climate.stress.test)
```

The raw and matched loan book files need to be run through PACTA for banks and
wrangled into the specific input format required by `r2dii.climate.stress.test`.
To make this process as easy as possible for the user, we provide a function,
`run_prep_calculation_loans()`, which takes care of all relevant steps with
minimal input from the user.

**NOTE:** We strongly recommend providing the matched and prioritized loan book
in one file for the entire raw loan book to be analyzed. In PACTA for banks, it
can sometimes be advantageous for matching to split the loan book into separate
files for each sector (or other splits). This should be avoided here, since the
function also calculates relative exposures. Hence, after completing the steps
of matching and prioritizing the loan book, all prioritized files should be
combined into one file, before running this function.

The r2dii.climate.stress.test currently supports a number of scenario geographies 
and four of the PACTA for Banks sectors of company production. They are the following:

```{r}
sectors <- unique(scenario_geography_x_ald_sector$ald_sector)
print(sectors)
```

Note that the supported sectors do depend on the `scenario_geography` 
(i.e. the geographical region (concerning asset location) results shall be 
calculated for).
All supported scenario geographies are the following:
```{r}
scenario_geographies <- unique(scenario_geography_x_ald_sector$scenario_geography)
print(scenario_geographies)
```

You can use a helper function to obtain the supported scenario_geographies for
a sector as follows:
  
```{r}
geographies_for_sector("Coal")
```

Beside the file paths, the only argument that can be set is `credit_type`, which
defaults to `"outstanding"` if the user passes no argument.

View other options by running:

```{r}
credit_type_lookup
```

If everything has been set up correctly, simply running the following command in
R will read the raw and matched loan books from the indicated project-specific
inputs directory and auxiliary data from the project-agnostic data directory.

It will then perform all calculations and wrangling required and write the
intermediate input files `Loans_results_company.rda` and
`overview_portfolio.rda` to the indicated `data_prep_output_path`. 
**NOTE:** Data generated with this workflow will serve as inputs for the
subsequent stress test. Thus it is advisable to set `data_prep_output_path` to
the same path as `input_path_project_specific` so that the generated data is
written there.

```{r, eval=FALSE}
run_prep_calculation_loans(
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  data_prep_output_path = "/example_project/project_specific_input/",
)
```

Since the argument credit_type has a default value, it is not required to set it,
in case the user wants to run the stress test on the outstanding credit values
in the loan book.

However, it is also possible to run the analysis on the credit limits of the
loans, in case these have been provided in the raw and matched loan books. To
achieve this, instead of the previous command, simply run:

```{r, eval=FALSE}
run_prep_calculation_loans(
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  data_prep_output_path = "/example_project/project_specific_input/",
  credit_type = "credit_limit"
)
```

## Next steps

Regardless of which case is chosen, the intermediate input files are generated
in the correct format so that the user can directly continue with the main
calculation of the stress test, as described in vignette [Run stress test](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/03-run-stress-test.html).
