---
title: "03 - Run transition risk stress test on corporate loan books"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette describes in detail, how to run a climate transition risk stress
test for loans, using the function `run_stress_test` to calculate the credit risk
of a loan book.

## Assumptions

In order to keep this vignette concise, we assume the following has been set up:

1. R and RStudio are installed.
2. All required R packages are installed, specifically
`r2dii.climate.stress.test`. Note that this may require installing additional
packages. You will be prompted to install these in case any are missing.
3. The user has successfully run at least the matching part of PACTA for Banks
to produce the relevant project-specific raw input files.
4. The user has obtained all relevant input files as described in the pdf manual.
5. The input files are organized in a folder structure consistent with the one
described in the vignette [Set up project directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).
6. The user has successfully run the function `run_prep_calculation_loans()` to
generate the intermediate input files for the main stress test function in the
required format. Refer to the [corresponding vignette](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html)
for details on how to do this.

## Running the Analysis

The climate transition risk stress test can be run for a single set of
parameters with one value per input argument or as a sensitivity analysis, where
one of the input arguments is iterated over and gets a vector of parameters and
all other arguments get one input value each. We will look at both cases.

Use `library()` to attach the package

```{r setup}
library(r2dii.climate.stress.test)
```

## Running the Stress Test for one scenario

In order to run a stress test for loans on one set of parameters, the user needs
to pass exactly one value per input argument to the function `run_stress_test()`.
The only arguments that do not have a default value and must be set by the user
are `asset_type` and the file paths. In this case, we want to run the stress
test for loans, so the easiest way to obtain results is by running:

```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  output_path = "/example_project/output",
)
```

This will calculate the stress test for loans and write the results along with a
log file into the designated output directory, using the default values for all
detail arguments.

**NOTE:** The default mode will **not return** any objects within the R session.
We find this is the easiest and most user friendly way to obtain results. We
alternatively provide the option that the function returns a list holding the
result objects. This allows the user to inspect and further analyze the data
directly in R.


### Input arguments
Specifications on the detail arguments are summarized in the following overview.
The defaults that are used if the argument is not adjusted when calling
`run_stress_test()` can be found in column `default`. The user may change any
detail argument by explicitly passing it to the function. Note that there are
allowed values for each of the inputs. For logical or character variables refer
to column `allowed`, for numeric variables the allowed values are the range from
`min` (inclusive) to `max` (inclusive).

```{r}
stress_test_arguments
```

Note that special special rules apply for the variables `baseline_scenario` and `shock_scenario`.
Baseline and shock scenarios can in principle be selected from the following:

```{r}
scenarios <- unique(scenario_geography_x_ald_sector$scenario)
print(scenarios)
```

Which scenarios are supported however depends on the analysed `sector` and
`scenario_geography`. In [the vignette on loan book preparation](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html)
we explained how to infer which combinations of `sector` and
`scenario_geography` are supported by the stress test. To infer which scenarios 
are supported for these combinations you can use the following helper function:
```{r}
scenario_for_sector_x_geography("Coal", "Europe")
```

**NOTE:** It is **strongly recommended** to select a `baseline_scenario` and a
`shock_scenario` from the same scenario source, as indicated by the part of the
scenario name in front of the underscore symbol.

### Understanding the input arguments
The meaning of each of the detail arguments is as follows:

* `baseline_scenario` holds the name of the baseline scenario to be used in the
stress test. We use a business-as-usual scenario for the baseline.
* `shock_scenario` holds the name of the scenario that companies are forced to
transition to via a late and sudden shock. We use an ambitious transition
scenario as the shock scenario. (**NOTE:** In almost all use cases, it is
advisable to use baseline and shock scenarios from the same scenario source. We
do not recommend deviating from that, if you do not have a very particular
reason to do so.)
* `lgd` is the loss given default used in the expected loss
calculation.
* `risk_free_rate` the risk free interest rate. Input parameter to the Merton
credit risk model.
* `discount_rate` the annual rate at which future cash flows are discounted when
calculating the net present value of companies in the loan book. Since the net
present values are indirect inputs into the Merton credit risk model, this
parameter my be relevant.
* `growth_rate` the perpetual 'economic' growth rate used in the discounted 
cash flow model for the calculation of terminal value of each firm in end_year + 1.
Must be positive and strictly smaller than discount_rate.
* `div_netprofit_prop_coef` coefficient that indicates what share of the net
present value should be considered to derive the equity value of a company.
* `shock_year` year in which the policy is introduced, that adjusts the
production values of companies to stay in line with carbon budgets.
* `fallback_term` indicates which maturity the loans in the loan book are
assumed to have. At this point we assume these are rolled over every year.
* `scenario_geography` indicates which geographical region(s) (concerning asset
location) results shall be calculated for.
* `use_company_terms_arg` logical parameter, indicating if individually provided
terms for companies as configured in company_terms.csv shall be used instead of
fallback as provided in `fallback_term`. The default is FALSE. For more details
compare ["Advanced data
settings"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/04-advanced-data-settings.html).
* `return_results` Logical parameter that indicates if the outputs of the
analysis should be directly written to the indicated output path or simply
returned as a list of results within the running session. The default is FALSE,
which writes the outputs to the target directory and does not return them as a
list object in R.

### Adjusting the input arguments
The user may want to run a stress test that is tailored to their assumptions
about a plausible transition risk shock scenario. For example, the user could
decide to set a lower `risk_free_rate` and shock the companies earlier than by
default, using:

```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  output_path = "/example_project/output",
  risk_free_rate = 0.01,
  shock_year = 2028
)
```

**NOTE:** One important input argument that affects the behavior of where the
results are written, is the argument `return_results`. Per default it is set to
`FALSE`, which means that results are written as csv files to a sub directory in
the `output_path` and the user must open these files to view the results.
If the user wants to view the results directly in R, they can set the argument
to `TRUE` which will return them as a list of data frames in the R session. This
means they are not written to the designated `output_path` however, so the user
must do this by themselves if the results ought to be kept. In this case, the
user must still provide an output path though, as every calculation will write a
log file.

### Output files
The output files are written into a sub directory of the path indicated as
`output_path` in the function call. The name of the sub directory is created
from the time stamp of the analysis and a suffix. The suffix `_standard` is used
when each argument uses a single parameter value. If a sensitivity analysis (see
below) is run the name of the varied detail variable is used. The sub directory
will be generated automatically, this way we ensure that no existing results are
overwritten.

* `log_file_standard.txt`
* `loans_company_trajectories_\<suffix\>.csv`
* `loans_portfolio_value_changes_standard.csv`
* `loans_company_value_changes__standard.csv`
* `loans_company_expected_loss_standard.csv`
* `loans_sector_pd_changes_annual_standard.csv`
* `loans_sector_pd_changes_overall_standard.csv`
* `loans_company_pd_changes_annual_\<suffix\>.csv`
* `loans_company_pd_changes_overall_\<suffix\>.csv`

## Running a Sensitivity Analysis for the Stress Test

In case the user wants to understand the sensitivities of the model to the input
parameters mentioned above, it is straight forward to run a sensitivity analysis
that does exactly that.

In order to do that, one simply passes a vector of allowed values for one (and
only one) of the detail arguments when running the stress test function. This
will lead to the model iterating over the set of values passed for the chosen
argument, while keeping all other input arguments constant.

**NOTE:** It is not possible to iterate over `asset_type` and `term`.

If the user wishes to understand the impact of the `shock_year` on the results
for example, they can run the following:

```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  output_path = "/example_project/output",
  shock_year = c(2025, 2028, 2032, 2035)
)
```

This will yield outputs with four versions of the stress test, one for each of
the shock years indicated. All the results will be written into one file per
output type for ease of use, e.g.:

* `loans_portfolio_value_changes_shock_year.csv`
* `loans_company_value_changes_shock_year.csv`
* `loans_company_expected_loss_shock_year.csv`
* `loans_sector_pd_changes_annual_shock_year.csv`
* `loans_sector_pd_changes_overall_shock_year.csv`

**NOTE:** The suffix of the files is now changed to mirror which variable was
iterated over. This enables the user to run multiple different sensitivity
analyses for a project and easily navigate these.

When running a sensitivity analysis one one input, the user can still use other
values than the default parameters for the other input arguments.

For example, when iterating over the `shock_year`, it is still possible to use a
`risk_free_rate` lower than the default like so:

```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/example_project/project_specific_input/",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  output_path = "/example_project/output",
  risk_free_rate = 0.01,
  shock_year = c(2025, 2028, 2032, 2035)
)
```

**NOTE** that the selected detail arguments will be written to the result files
so that it is always possible to understand which parameters were used in any
given calculation.

## Interpretation of the output files

Detailed explanations of the result files can be found in the vignette:
[Understand the output files of the transition risk stress test](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/05-read-the-outputs.html).
