---
title: "04 - Improve stress test by providing further project specific data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignettes describes in detail how an analysis can be configured further by
providing your own dataset for term values on company level. The configurations
are not necessary but, in case required information is available, may help you
improve the accuracy of your results.

## Prerequisites
In order to keep this vignette concise, we assume that you have successfully
complete all preparation steps described in the vignettes ["Set up project
directories"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html)
and [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html)


## Company - term data
Including company - term data allows you to incorporate the information you have
on the term values of the companies in your portfolio, instead of using an
identical term value for all companies.

### Preparing company - term data
The data that needs to be created is a csv file named company_terms.csv. It
holds the columns `company_name` (character, holding name of analysed companies)
and term (numeric, indicates which maturity the loans to respective company is
assumed to have in years). In column `company_name` include all unique company names from
`Loans_results_company.rda`, which you generated in [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).
If you want to use R to obtain this column you can take the following steps.

```{r, eval = FALSE}
library(readr)
data <- readr::read_rds(file.path("/path/to/specific/data/inputs", "Loans_results_company.rda"))
unique_companies <- data %>%
  dplyr::select(company_name) %>%
  dplyr::distinct()
readr::write_csv(unique_companies, file.path("/path/to/specific/data/inputs", "company_terms.csv"))

```

You can now open this file in a tool of your choice, and add second column
named term. In term add the terms per company.   

**NOTE:** 

* Terms need to be whole numbers. 
* Only include values up to 5. Higher values will be capped to 5 as predictions
for longer time frames the reliability of model deteriorates.
* leave term  blank for companies for which you lack respective information. A
fallback, as provided as argument `term` to `run_stress_test()` will be used to
fill the gaps.

### Validating company - term data
Before including the file in your analysis you may want to validate that your
file complies with requirements concerning structure and content. You may verify
by executing the following lines of code.
```{r, eval = FALSE}
library(r2dii.climate.stress.test)
data <- readr::read_csv(file.path("/path/to/specific/data/inputs", "company_terms.csv"))


```

### Placing file in folder structure

### Running the Stress Test with provided company - term data
```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/path/to/specific/data/inputs",
  input_path_project_agnostic = "/path/to/agnostic/data",
  output_path = "/path/to/output/directory",
  use_company_terms = TRUE
)
```
