---
title: "04 - Improve stress test by providing further project specific data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignettes describes in detail how an analysis can be configured further by
providing your own dataset for term values on company level. The configurations
are not necessary but, in case required information is available, may help you
improve the accuracy of your results.

## Prerequisites
In order to keep this vignette concise, we assume that you have successfully
complete all preparation steps described in the vignettes ["Set up project
directories"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html)
and [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html)


## Company - term data
Including company - term data allows you to incorporate the information you have
on the term values of the companies in your portfolio, instead of using an
identical term value for all companies.


### Preparing company - term data

### Validating company - term data

### Running the Stress Test with provided company - term data
```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/path/to/specific/data/inputs",
  input_path_project_agnostic = "/path/to/agnostic/data",
  output_path = "/path/to/output/directory",
  use_company_terms = TRUE
)
```
