---
title: "04 - Improve stress test by providing further project specific data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette describes in detail how an analysis can be configured further by
providing more custom data. The configurations are not required but, in case
additional information is available, may help you improve the accuracy of your
results.

## Assumptions

In order to keep this vignette concise, we assume the following has been set up:

1. R and RStudio are installed.
2. All required R packages are installed, specifically
`r2dii.climate.stress.test`. Note that this may require installing additional
packages. You will be prompted to install these in case any are missing.
3. The user has successfully run at least the matching part of PACTA for Banks
to produce the relevant project-specific raw input files.
4. The user has obtained all relevant input files as described in the pdf manual.
to produce the relevant project-specific raw input files.
5. The input files are organized in a folder structure consistent with the one
described in the vignette [Set up project directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).
6. The user has successfully run the function `run_prep_calculation_loans()` to
generate the intermediate input files for the main stress test function in the
required format. Refer to the [corresponding vignette](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html)
for details on how to do this.

## Prerequisites
In order to keep this vignette concise, we assume that you have successfully
completed all preparation steps described in the vignettes [Set up project
directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html)
and [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).


## Company - term data
Including company - term data allows you to incorporate the information you have
on term values of the loan to a company in your loan book, instead of using an
identical term value for all loans.

### Preparing company - term data 
The data that needs to be created is a csv file named `company_terms.csv`. It
holds the columns `company_name` (character, holding the name of analysed
companies) and term (numeric, indicates which maturity the loans to respective
companies is assumed to have in years). In column `company_name` include all
unique company names from `Loans_results_company.rda`, which you generated in
[prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).
If you want to use R to obtain this column you can take the following steps.

```{r, eval = FALSE}
library(readr)
library(r2dii.climate.stress.test)

loans_results_company_file_path <- file.path("/example_project/project_specific_input", "Loans_results_company.rda")
validate_file_exists(loans_results_company_file_path)
data <- readr::read_rds(loans_results_company_file_path)
unique_companies <- data %>%
  dplyr::select(company_name) %>%
  dplyr::distinct()
readr::write_csv(unique_companies, file.path("/example_project/project_specific_input", "company_terms.csv"))

```

You can now open this file in a tool of your choice, and add second column named
term. In column `term` add the terms per company. Please make sure to save the
result as a csv file again. Make sure that file is saved in folder holding
project specific data.

**NOTE:** 

* Terms need to be whole numbers. 
* Only include values up to 5. Higher values will be capped to 5 as for
calculations with longer time frames the reliability of the Merton model
deteriorates.
* Leave term blank for companies for which you lack respective information. A
fallback, as provided as argument `fallback_term` to `run_stress_test()` will be
used to fill the gaps.

### Validating company - term data
Before including the file in your analysis you may want to validate that your
file complies with requirements concerning structure and content. You may verify
by executing the following lines of code. You will receive warning/error
messages in case problems are detected.
```{r, eval = FALSE}
library(readr)
library(r2dii.climate.stress.test)

company_terms_path <- file.path("/example_project/project_specific_input", "company_terms.csv")
validate_file_exists(company_terms_path)
data <- readr::read_csv(company_terms_path)
validate_data_has_expected_cols(data = data, expected_columns = c("company_name", "term"))
check_company_terms(data = data, interactive_mode = TRUE)
```

### Placing file in folder structure
In order to make sure your version of `company_terms.csv` is used in the
analysis place it in

* `example_project/`
    * `project_specific_input`
    
as set up in [Set up project
directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).

### Running the Stress Test with provided company - term data
In order to include the company - term data in your analysis set argument
`use_company_terms` to TRUE in the call to `run_stress_test`.
```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/example_project/project_specific_input",
  input_path_project_agnostic = "/example_project/project_agnostic_input/",
  output_path = "/example_project/output",
  use_company_terms = TRUE
)
```

## Financial data
Financial data provide several financial indicators on the company level. If
data is available you can replace our standard financial data set with a data
set holding your financial information on the companies you included in the
analysis.  

### Preparing financial data
The data that needs to be created is a csv file named
`prewrangled_financial_data_stress_test.csv`to replace the default
`prewrangled_financial_data_stress_test.csv` file.
It holds the columns:

* `company_name`: character, holding the name of analysed companies.
* `company_id`: numeric, the id of company as classified by asset resolution.
For loans workflow a placeholder value will be used.
* `corporate_bond_ticker`: character, holding the identifier. Will be NA for
loans workflow.
* `pd`: numeric, holding the probability of default per company. Needs to be
equal to or larger than 0 and smaller than 1.
* `net_profit_margin`: numeric, holding the net_profit_margin per company. Needs
to be larger than 0 and equal to or smaller than 1.
* `debt_equity_ratio`: numeric, holding the ratio of outstanding debt to the
company's equity value. This is the company's financial leverage. Needs to be
larger than 0. 
* `volatility`: numeric, holding the volatility of asset. Needs to be equal to
or larger than 0.

**NOTE**: No column, except for corporate_bond_ticker, may have missing values.

In column `company_name` include all unique company names from
`Loans_results_company.rda`, which you generated in [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).
Running the following code will generate a dataset with all required columns.
Column `campany_name` includes the unique company names, `company_id` includes a
placeholder id, all other columns are empty.

```{r, eval = FALSE}
library(readr)
library(r2dii.climate.stress.test)

loans_results_company_file_path <- file.path("/example_project/project_specific_input", "Loans_results_company.rda")
validate_file_exists(loans_results_company_file_path)
data <- readr::read_rds(loans_results_company_file_path)
fin_companies <- data %>%
  dplyr::select(company_name) %>%
  dplyr::distinct() %>% 
  dplyr::mutate(
    company_id = 999, 
    corporate_bond_ticker = NA,
    pd = NA,
    net_profit_margin = NA,
    debt_equity_ratio = NA,
    volatility = NA)
readr::write_csv(fin_companies, file.path("/example_project/project_agnostic_input", "prewrangled_financial_data_stress_test.csv")) # NOTE that this will overwrite financial data currently stored at the location if available
```

You can now open this file in a tool of your choice and fill in values for the
remaining variables. For column `company_id` keep using a placeholder value
(999 in example) and leave entries for `corporate_bond_ticker`as NA. Please make
sure to save the result as a csv file again.

### Validating financial data
Before including the file in your analysis you may want to validate that your
file complies with requirements concerning structure and content. You may verify
by executing the following lines of code. You will receive warning/error
messages in case problems are detected.
```{r, eval = FALSE}
library(readr)
library(r2dii.climate.stress.test)

financial_data_path <- file.path("/example_project/project_agnostic_input",
                                 "prewrangled_financial_data_stress_test.csv")
validate_file_exists(financial_data_path)
data <- readr::read_csv(financial_data_path)
check_financial_data(financial_data = data, asset_type = "loans", interactive_mode = TRUE)

```

### Placing file in folder structure
In order to make sure your version
of `prewrangled_financial_data_stress_test.csv` is used in the analysis place it
in

* `analysis_input_files/`  
    
as set up in [Set up project
directories](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).
If the respective dataset as provided by 2DII already exists there make sure to 
replace it with your custom file.

### Running the Stress Test with provided financial data
You can now run the stress test as described in vignette [Run stress test](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/03-run-stress-test.html).
