---
title: "04 - Improve stress test by providing further project specific data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette describes in detail how an analysis can be configured further by
providing more custom data. The configurations are not required but, in case
additional information is available, may help you improve the accuracy of your
results.

## Prerequisites
In order to keep this vignette concise, we assume that you have successfully
completed all preparation steps described in the vignettes ["Set up project
directories"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html)
and ["prepare loans
inputs"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).


## Company - term data
Including company - term data allows you to incorporate the information you have
on term values of the loan to a company in your loan book, instead of using an
identical term value for all loans.

### Preparing company - term data
The data that needs to be created is a csv file named `company_terms.csv`. It
holds the columns `company_name` (character, holding name of analysed companies)
and term (numeric, indicates which maturity the loans to respective companies is
assumed to have in years). In column `company_name` include all unique company
names from `Loans_results_company.rda`, which you generated in [prepare loans
inputs](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/02-prepare-loans-inputs.html).
If you want to use R to obtain this column you can take the following steps.

```{r, eval = FALSE}
library(readr)
library(r2dii.climate.stress.test)

loans_results_company_file_path <- file.path("/path/to/specific/data/inputs", "Loans_results_company.rda")
validate_file_exists(loans_results_company_file_path)
data <- readr::read_rds(loans_results_company_file_path)
unique_companies <- data %>%
  dplyr::select(company_name) %>%
  dplyr::distinct()
readr::write_csv(unique_companies, file.path("/some/path", "company_terms.csv"))

```

You can now open this file in a tool of your choice, and add second column named
term. In column `term` add the terms per company. Please make sure to save the
result as a csv file again.

**NOTE:** 

* Terms need to be whole numbers. 
* Only include values up to 5. Higher values will be capped to 5 as for
calculations with longer time frames the reliability of the Merton model
deteriorates.
* Leave term blank for companies for which you lack respective information. A
fallback, as provided as argument `term` to `run_stress_test()` will be used to
fill the gaps.

### Validating company - term data
Before including the file in your analysis you may want to validate that your
file complies with requirements concerning structure and content. You may verify
by executing the following lines of code.
```{r, eval = FALSE}
library(r2dii.climate.stress.test)

company_terms_path <- file.path("/path/to/file")
validate_file_exists(company_terms_path)
data <- readr::read_csv(company_terms_path)
validate_data_has_expected_cols(data = data, expected_columns = c("company_name", "term"))
check_company_terms(data = data, interactive_mode = TRUE)

```

### Placing file in folder structure
In order to make sure `company_terms.csv` can be included in the analysis place
it in

* `example_folder/`
    * `inputs/`  
    
as set up in ["Set up project
directories"](https://2degreesinvesting.github.io/r2dii.climate.stress.test/articles/articles/01-setup-project-directories.html).

### Running the Stress Test with provided company - term data
In order to include the company - term data in your analysis set argument
`use_company_terms` to TRUE in the call to `run_stress_test`.
```{r, eval = FALSE}
run_stress_test(
  asset_type = "loans",
  input_path_project_specific = "/path/to/specific/data/inputs",
  input_path_project_agnostic = "/path/to/agnostic/data",
  output_path = "/path/to/output/directory",
  use_company_terms = TRUE
)
```
