---
title: "Prepare inputs for stress testing loans"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Preparing the inputs for stress testing loan books

This vignette describes in detail, how to prepare the required input files
needed to run the climate transition risk stress test to calculate the credit
risk of a loan book.

## Assumptions

In order to keep this vignette concise, we assume the following has been set up:

1. R and RStudio are installed
2. All required R packages are installed, this specifically includes
`r2dii.data`, `r2dii.match`, `r2dii.analysis` and `r2dii.climate.stress.test`
1. The user has obtained all relevant input files as described in the pdf manual
1. The input files are organized in a folder structure consistent with the manual
1. This notably implies the user has successfully run at least the matching
part of PACTA for banks to produce the relevant project-specific input files
1. The user has set up objects that point to the input directories for
project-specific and project-agnostic input files.

Once all these requirements are met, we can produce the intermediate input files
required for a climate transition risk stress test of corporate loans.

## Running the Loan Book Preparation

```{r setup}
library(r2dii.climate.stress.test)
```

The raw and matched loan book files need to be run through PACTA for banks and
wrangled into the specific inout format required by `r2dii.climate.stress.test`.
To make this process as easy as possible for the user, we provide a function,
`run_prep_calculation_loans()`, which takes care of all relevant steps with
minimal input from the user.

The only orgument that can be set is `credit_type`, which defaults to
`"outstanding"` if the user passes no argument. View other options by running:

```{r}
credit_type_lookup
```

If everything has been set up correctly, simply running the following command in
R will read the raw and matched loan books from the indicated project-specific
inputs directory, perform all calcualtions and wrangling required and write the
intermediate input files `Loans_results_company.rda` and `overview_portfolio.rda`
to the same input file directory.

```{r}
# run_prep_calculation_loans()
```

Since the argument credit_type has a default value, it is not required to set it,
in case the user wants to run the stress test on the outsatnding credit values
in the loan book.

However, it is also possible to run the analysis on the credit limits og the
loans, in case these have been provided in the raw and matched loan books. To
achieve this, instead of the previous command, simply run:

```{r}
# run_prep_calculation_loans(credit_type = "credit_limit")
```

Regardless of which case is chosen, the intermediate input files are generated
in the correct format and directory to directly continue with the main stress
test calculation as described in vignette **LINK**
